### 2017-01-27 thesis/latex/thesis.tex
Thesis: Add intro suggestions and a todo list.

\section{Chapter: Introduction}
\subsection{What is dynein?}
\subsubsection{Basics}

@@

\section{Questions for David}
\begin{itemize}
\item Would it be possible to, for the ET test, also verify the standard deviation of energy is what it should be? Since just verifying the energy averages to N/2KbT doesn't verify the forces are correct, but the stdev would?
\item What is the value of $\left<\Delta G_{conf}\right>$ in going from bothbound to onebound?
\end{itemize}
\end{document}

>>>>

\section{Chapter: Introduction}
Begin with a paper-like introduction which talks about:

\begin{itemize}
\item How dynein is a structure which turns chemical energy into motion
\item How it's weird that a cellular structure can generate directed motion
\item Other cool stuff - make dynein mysterious and cool.
\end{itemize}

\subsection{What is dynein?}
\subsubsection{Basics}

@@

\section{Questions for David}
\begin{itemize}
\item Would it be possible to, for the ET test, also verify the standard deviation of energy is what it should be? Since just verifying the energy averages to N/2KbT doesn't verify the forces are correct, but the stdev would?
\item What is the value of $\left<\Delta G_{conf}\right>$ in going from bothbound to onebound?
\end{itemize}

\section{Todo for project}
\begin{itemize}
\item Do calculations to turn processivity into state time ratios
\item Fit the state times to above number by tweaking un/binding rates
\item Fit spring constants to step length histograms
\end{itemize}
\end{document}
